method

### 2021-09-01 06_Paper/ER-ED/method.Rmd
added 2.1

## 2.1 Participants

Participants

>>>>

## 2.1 Sampling plan

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
